---
title: "R Notebook"
output: html_notebook
---

```{r}
dir.create("data")
download.file(
  url = "http://files.grouplens.org/datasets/movielens/ml-latest.zip", 
  destfile = "data/ml-latest.zip"
)
unzip("data/ml-latest.zip", exdir = "data")
```

```{r}
# read in the csv files
movies <- read.csv("data/ml-latest/movies.csv")  # movie info: title and genre
ratings <- read.csv("data/ml-latest/ratings.csv") # user ratings for each movie
tags <- read.csv("data/ml-latest/tags.csv") # additional user reviews ("tag")
links <- read.csv("data/ml-latest/links.csv") # lookup for imdb movie IDs

# save as .RData
save(links, movies, ratings, tags, file = "data/movielens.RData")
```

```{r}
load("data/movielens.RData")
```

```{r}
library(tidyverse)
library(NNLM)
library(tictoc)
```

Looking at the data
```{r}
glimpse(ratings)
```


```{r}
length(unique(ratings$userId))
unique(ratings$rating)
length(unique(movies$movieId))
length(unique(movies$title))
```

From the length of the unique "movieId" and "title" above, we see that some titles are associated with more than one movieId. There are 78 such duplicates, It was decided that the duplicates would be removed. This is executed in the chuck below.
```{r}
movies <- distinct(movies, title, .keep_all = T)
```


```{r}
Ratings <- left_join(ratings, movies) 
Ratings <- na.omit(Ratings)
Ratings
```

This functions creates a subset of the movie dataset, using the required number of users and movies, and a specified seed for replication. 
```{r}
Data_Subset <- function(data, no_of_users, no_of_movies, seed){
  #data - the dataframe of the movie ratings
  #no_of_users - scalar value, the number of users to be sampled at random from the full dataset
  #no_of_movies - scalar value, the number of movies to sample. The movies shall be sampled in descending order to gain as much information as possible
  #seed - the set seed needed for reproducing results. 
  
  #movies_frq is the total number of ratings for each movie received, arranging in descending order to capture the top rated movies for the subset
  movies_frq <- data %>% group_by(movieId) %>% summarize(count = n()) %>% arrange(desc(count)) 
  Movies <- movies_frq$movieId[1:no_of_movies]
  
  #users_frq is the total number of ratings for each user gave, which will be sampled randomly according to the specified seed.
  users_frq <- data %>% group_by(userId) %>% summarize(count = n()) %>% arrange(desc(count))
  set.seed(seed)
  Users <- sample_n(users_frq, size = no_of_users, replace = F) %>% select(userId)
  
  
  Data_SubSet <- data %>% filter(userId %in% (Users$userId), movieId %in% Movies) %>% droplevels()
  return(Data_SubSet)
}
```

## Cosine similarity function
```{r}
tic("Cosine_Sim1")
cosine_sim <- function(a){
  #a - the matrix on which cosine similarity will be performed on. 
  #b - the output matrix of the cosine similarity function
  
  a <- ifelse(is.na(a), 0, a)
  b <- tcrossprod(a/sqrt(rowSums(a^2)))
  diag(b) <- 0
  row.names(b) <- row.names(a) #copying the names from the original matrix to label the new matrix
  colnames(b) <- row.names(a)
  
  return(as.matrix(b))
}

toc()
```

User-based and by extension item based. This is specifically to predict the ratings for the values in the test set to calculate the RMSE
```{r}
  UB_predicted <- NULL

  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])
    title <- as.character(test$title[i])
    sim <- user_sim[user,]
    rate <- Movie_rating[,title]
    
    sim_to_user <- as.data.frame(na.omit(cbind(sim, rate)))
    scaled_sim <- sim_to_user$sim/sum(sim_to_user$sim)
    sim_to_user <- cbind(sim_to_user,scaled_sim)
    UB_predicted[i] <- crossprod(sim_to_user$rate,scaled_sim)
    UB_predicted[i] <- ifelse(is.nan(UB_predicted[i]) == T, mean(sim_to_user$rate), UB_predicted[i])
  }
```


#Matrix Factorization with bias and Regularisation
```{r}
MF_TestPrediction <- function(Movie_rating, test){
  #H0 and W0 are the bias matrices, that are set to an initial value of 1.
init = list(
  H0 = matrix(1, nrow = 1, ncol = ncol(Movie_rating)),
  W0 = matrix(1, nrow = nrow(Movie_rating), ncol = 1)
)

# matrix factorization with bias included
decomp <- nnmf(A = Movie_rating,
               method = "scd",
               k = 3,
               alpha = c(0.001,0,0),  #L2 Regularisation on W 
               beta = c(0.001,0,0),   #L2 Regularisation on H
               init = init, # bias terms
               max.iter = 10000) #Maximum number of iterations

# results
mf_observed <- decomp$W %*% decomp$H  #predicted values of all the movie & user combinations

#This function extracts the predictions of the test set observations.
Prediction <- function(i){   
  user <- as.character(test$userId[i])
  title <- as.character(test$title[i])
  Predicted <- NULL
  
  Predicted[i] <- mf_observed[user, title]
  Predicted[i] <- ifelse(Predicted[i] < 1, 1, Predicted[i]) #if the prediction is less than 1, if should be limited to 1
  Predicted[i] <- ifelse(Predicted[i] > 5 , 5, Predicted[i]) #if the prediction is greater than 5, if should be limited to 5
}


r = nrow(test)
MF_Predicted <- sapply(1:r, Prediction)  #this runs multiple values through the prediction function
 

return(MF_Predicted)
}
```

```{r}
Fulltest <- function(seed, no_of_users, data, no_of_movies){
  Reduced_Ratings <- Data_Subset(data, no_of_users, no_of_movies, seed)
  
  set.seed(seed) #USing the same seed for all iterations
  testobs <- sample(nrow(Reduced_Ratings),trunc(length(Reduced_Ratings$rating)*0.1)) #sampling 10% of points to form the test set
  
  test <- Reduced_Ratings[testobs,]  #saving the test set and its values
  
  Reduced_Ratings$rating[testobs] <- NA  # setting them to NA for the model to predict
  
  Movie_rating <- Reduced_Ratings %>% 
    complete(userId, title) %>% 
    select(userId, title, rating) %>% 
    spread(key = title, value = rating)
  
  sorted_users <- as.character(unlist(Movie_rating[,1]))
  Movie_rating <- as.matrix(Movie_rating[,-1])
  row.names(Movie_rating) <- sorted_users
  
  user_sim <- cosine_sim(Movie_rating)
  
  predictedA <- NULL

  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])
    title <- as.character(test$title[i])
    sim <- user_sim[user,]
    rate <- Movie_rating[,title]
    
    sim_to_user <- as.data.frame(na.omit(cbind(sim, rate)))
    scaled_sim <- sim_to_user$sim/sum(sim_to_user$sim)
    sim_to_user <- cbind(sim_to_user,scaled_sim)
    predictedA[i] <- crossprod(sim_to_user$rate,scaled_sim)
    predictedA[i] <- ifelse(is.nan(predictedA[i]) == T, mean(sim_to_user$rate), predictedA[i])
  }
  
  movies_user <- t(Movie_rating)
  movie_sim <- cosine_sim(movies_user)
  
  predictedB <- NULL


  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])
    title <- as.character(test$title[i])
    sim <- movie_sim[title,]
    rate <- movies_user[,user]
    
    sim_to_movie <- as.data.frame(na.omit(cbind(sim, rate)))
    scaled_movie_sim <- sim_to_movie$sim/sum(sim_to_movie$sim)
    sim_to_movie <- cbind(sim_to_movie,scaled_movie_sim)
    predictedB[i] <- crossprod(sim_to_movie$rate,scaled_movie_sim)
    predictedB[i] <- ifelse(is.nan(predictedB[i]) == T, mean(sim_to_movie$rate), predictedB[i])
  }
  
  predictedC <- MF_TestPrediction(Movie_rating, test)
  
  PredictedD <- apply(cbind(predictedA,predictedB, predictedC), 1, mean)

  RMSE_PredD <- sqrt(sum((PredictedD - test$rating)^2)/length(test$rating))
  return(RMSE_PredD) 
}
```

```{r}
tic("test1")
Fulltest(Ratings, no_of_users = 100, no_of_movies = 1000, seed = 100)
toc()
```


```{r}
tic("Simulation")
accuracy300 <- NULL
for (i in 1:21){
  seed <- c(1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,33,35,37,39, 100)
  accuracy300[i] <- Fulltest(Ratings, no_of_users = 300, no_of_movies = 1000, seed = seed[i])
}
toc()
accuracy300
rt <- t(as.matrix(accuracy300))
```

```{r}
tic()
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)
# c(1,101,525,69, 73)
# 

accuracy100users <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 1000, seed = seed[i]))
accuracy100users
toc()
```

```{r}
tic()
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)

accuracy500users <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 1000, seed = seed[i]))
accuracy500users
toc()
```

```{r}
#run again
tic()
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)

accuracy1000users <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 1000, seed = seed[i]))
accuracy1000users
toc()
```

```{r}
tic()
seed <- c(1,101,525,69,73)

accuracy3000users <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 1000, seed = seed[i]))
accuracy3000users
toc()
```

```{r}
tic()
seed <- c(1,101,525,69,73)

accuracy5000users <- sapply(1,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 1000, seed = seed[i]))
accuracy5000users
toc()
```

```{r}
accuracy5000users
```

```{r}

Range_for_1000movies <- cbind(summary(accuracy100users),summary(accuracy500users),summary(accuracy1000users),summary(accuracy3000users),summary(accuracy5000users))
colnames(Range_for_1000movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_1000movies, xlab = "No of Users", ylab = "RMSE", main = "Boxplots of different user counts for 1000 Movies",col = c("blue", "red", "green", "violet" , "yellow" ))
```

```{r}
x_axis = c(100, 500, 1000, 3000, 5000)
plot(x= x_axis, y = Range_for_1000movies[4,], type = "b", pch = 19, ylim = c(0.8, 1.2), lwd = 2, ylab = "RMSE", xlab = "No. of Users", main = "RMSE against the Number of User")
#points(Range_for_1000movies[4,])
lines(x= x_axis, y =Range_for_1000movies[1,], col = "darkgreen", lty = 2)
lines(x= x_axis, y =Range_for_1000movies[5,], col = "firebrick", lty = 2)
axis(1, at = c(1, 2, 3, 4, 5) ,labels=colnames(Range_for_1000movies))
# Add a legend
legend("topright", inset=.02, legend=c("Maximum", "Mean", "Minimum"), box.lty=0,
       col=c("firebrick", "black","darkgreen"), lty= c(2,1,2), lwd= c(1,2,1), cex=0.8, bg='lightblue')
```

```{r}
tic()
seed <- c(1,101,525,69, 73)

accuracy100users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 500, seed = seed[i]))
accuracy500users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 500, seed = seed[i]))
accuracy1000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 500, seed = seed[i]))
accuracy3000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 500, seed = seed[i]))
accuracy5000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 500, seed = seed[i]))
toc()
```


```{r}
save(accuracy100users, accuracy500users, accuracy1000users, accuracy3000users, accuracy5000users, accuracy100users500movies, accuracy500users500movies, accuracy1000users500movies, accuracy3000users500movies, accuracy5000users500movies, Range_for_1000movies,  file = "data/Results.RData")
load("data/Results.RData")
```

```{r}
Range_for_500movies <- cbind(summary(accuracy100users500movies),summary(accuracy500users500movies),summary(accuracy1000users500movies),summary(accuracy3000users500movies),summary(accuracy5000users500movies))
colnames(Range_for_500movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_500movies, xlab = "No of Users", ylab = "RMSE", main = "Boxplots of different user counts for 500 Movies",col = c("blue", "red", "green", "violet" , "yellow" ))
```

```{r}
x_axis = c(100, 500, 1000, 3000, 5000)
plot(x= x_axis, y = Range_for_500movies[4,], type = "b", pch = 19, ylim = c(0.8, 1.1), lwd = 2, ylab = "RMSE", xlab = "No. of Users", main = "RMSE against the Number of User for 500 movies")
lines(x= x_axis, y =Range_for_500movies[1,], col = "blue", lty = 2)
lines(x= x_axis, y =Range_for_500movies[5,], col = "red", lty = 2)
axis(1, at = c(1, 2, 3, 4, 5) ,labels=colnames(Range_for_500movies))
# Add a legend
legend("topright", inset=.02, legend=c("Maximum", "Mean", "Minimum"), box.lty=0,
       col=c("red", "black","blue"), lty= c(2,1,2), lwd= c(1,2,1), cex=0.8, bg='lightblue')
```

```{r}
Range_for_100movies <- cbind(summary(accuracy100users100movies),summary(accuracy500users100movies),summary(accuracy1000users100movies),summary(accuracy3000users100movies),summary(accuracy5000users100movies))
colnames(Range_for_100movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_100movies, xlab = "No of Users", col = c("blue", "red", "green", "violet" , "yellow" ))
```


```{r}
Range_for_1000movies
new_rnge
Range_for_500movies
```

```{r}
Set5_100 <- accuracy100users[c(1, 5, 12, 19, 20)]
Set5_500 <- accuracy500users[c(1, 5, 12, 19, 20)]
Set5_1000 <- accuracy1000users[c(1, 5, 12, 19, 20)]
new_rnge <- cbind(summary(Set5_100),summary(Set5_500),summary(Set5_1000),summary(accuracy3000users),summary(accuracy5000users))
```

```{r}
tic()
seed <- c(1,101,525,69, 73)

accuracy100users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 100, seed = seed[i]))
accuracy500users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 100, seed = seed[i]))
accuracy1000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 100, seed = seed[i]))
accuracy3000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 100, seed = seed[i]))
accuracy5000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 100, seed = seed[i]))
toc()
```

Checking the progression of the RMSE with respect to the number of movies sampled.The number of movies sampled were 100, 500 and 1000.
```{r}
RMSE_vs_Movies <- cbind(Range_for_100movies[4,], Range_for_500movies[4,] ,Range_for_1000movies[4,])
RMSE_vs_Movies
colindex = c("blue", "red", "green", "violet")

#plot of all the different user sizes
plot(x = c(100, 500, 1000), y = RMSE_vs_Movies[5,], type = "l", ylim = c(0.83,1.1), col = "yellow", main = "RMSE against the Number of Movies", xlab = "Number of Movies", ylab = "RMSE")
for (i in 1:4) {
  lines(x = c(100, 500, 1000), y = RMSE_vs_Movies[i,], col = colindex[i] )
}

legend("topleft", inset=.02, legend=c("100 users","500 users","1000 users","3000 users","5000 users"), box.lty=1,
       col=c(colindex, "yellow"), lty= 1, cex=0.8)


#plot of all the different user sizes excluding 100 users for a closer look
plot(x = c(100, 500, 1000), y = RMSE_vs_Movies[5,], type = "l", ylim = c(0.83,0.9), xlim = c(100,1000), col = "yellow", main = "RMSE against the Number of Movies", xlab = "Number of Movies", ylab = "RMSE")
for (i in 2:4) {
  lines(x = c(100, 500, 1000), y = RMSE_vs_Movies[i,], col = colindex[i] )
}

legend("topleft", inset=.02, legend=c("500 users","1000 users","3000 users","5000 users"), box.lty=1,
       col=c(colindex[2:4], "yellow"), lty= 1, cex=0.8)
```


