---
title: "R Notebook"
output: html_notebook
---

```{r}
dir.create("data")
download.file(
  url = "http://files.grouplens.org/datasets/movielens/ml-latest.zip", 
  destfile = "data/ml-latest.zip"
)
unzip("data/ml-latest.zip", exdir = "data")
```

```{r}
# read in the csv files
movies <- read.csv("data/ml-latest/movies.csv")  # movie info: title and genre
ratings <- read.csv("data/ml-latest/ratings.csv") # user ratings for each movie
tags <- read.csv("data/ml-latest/tags.csv") # additional user reviews ("tag")
links <- read.csv("data/ml-latest/links.csv") # lookup for imdb movie IDs

# save as .RData
save(links, movies, ratings, tags, file = "data/movielens.RData")
```

Loading data from a RData file, that is smaller in size than the original csv files
```{r}
load("data/movielens.RData")
```

Loading necessary libraries
```{r}
library(tidyverse)
library(NNLM)
library(tictoc)
```

Looking at the data
```{r}
glimpse(ratings)
```

Looking at the data contd.
```{r}
length(unique(ratings$userId))
unique(ratings$rating) #checking possible values of ratings
length(unique(movies$movieId))
length(unique(movies$title))
```

From the length of the unique "movieId" and "title" above, we see that some titles are associated with more than one movieId. There are 78 such duplicates, It was decided that the duplicates would be removed. This is executed in the chuck below.
```{r}
movies <- distinct(movies, title, .keep_all = T)
```

Creating a more detailed Ratings dataset, by including movie title and genre
```{r}
Ratings <- left_join(ratings, movies) 
Ratings <- na.omit(Ratings)
Ratings
```

This functions creates a subset of the movie dataset, using the required number of users and movies, and a specified seed for replication. 
```{r}
Data_Subset <- function(data, no_of_users, no_of_movies, seed){
  #data - the dataframe of the movie ratings
  #no_of_users - scalar value, the number of users to be sampled at random from the full dataset
  #no_of_movies - scalar value, the number of movies to sample. The movies shall be sampled in descending order to gain as much information as possible
  #seed - the set seed needed for reproducing results. 
  
  #movies_frq is the total number of ratings for each movie received, arranging in descending order to capture the top rated movies for the subset
  movies_frq <- data %>% group_by(movieId) %>% summarize(count = n()) %>% arrange(desc(count)) 
  Movies <- movies_frq$movieId[1:no_of_movies]
  
  #users_frq is the total number of ratings for each user gave, which will be sampled randomly according to the specified seed.
  users_frq <- data %>% group_by(userId) %>% summarize(count = n()) %>% arrange(desc(count))
  set.seed(seed)
  Users <- sample_n(users_frq, size = no_of_users, replace = F) %>% select(userId)
  
  
  Data_SubSet <- data %>% filter(userId %in% (Users$userId), movieId %in% Movies) %>% droplevels()
  return(Data_SubSet)
}
```

Cosine similarity function
```{r}
tic("Cosine_Sim1")
cosine_sim <- function(a){
  #a - the matrix on which cosine similarity will be performed on. 
  #b - the output matrix of the cosine similarity function
  
  a <- ifelse(is.na(a), 0, a)
  b <- tcrossprod(a/sqrt(rowSums(a^2))) #cosine similarity formula
  diag(b) <- 0   #setting the diagonals to 0, as the diagonals are a similarity comparison to themselves
  row.names(b) <- row.names(a) #copying the names from the original matrix to label the new matrix
  colnames(b) <- row.names(a)
  
  return(as.matrix(b))
}

toc()
```

User-based and by extension item based prediction process. This is specifically to predict the ratings for the values in the test set to calculate the RMSE
```{r}
  UB_predicted <- NULL

  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])   #selecting the user from the test set to predict rating for
    title <- as.character(test$title[i])   #selecting the corresponding movie from the test set
    sim <- user_sim[user,]      #the selected user's similarity vector
    rate <- Movie_rating[,title]   #the ratings for the corresponding movie
    
    #sim_to_user then combines the similarity vector and the available ratings, while omitting all users who haven't rated the movie
    sim_to_user <- as.data.frame(na.omit(cbind(sim, rate))) 
    scaled_sim <- sim_to_user$sim/sum(sim_to_user$sim)   #this scales the similarity values to sum up to 1. 
    sim_to_user <- cbind(sim_to_user,scaled_sim)
    
    #multiplying the ratings and the scaled similarity values gives a rating prediction between 1 and 5 
    UB_predicted[i] <- crossprod(sim_to_user$rate,scaled_sim)  
    
    #In the event, that a user is not similar to any of the users who have rated the movie, the average rating from the other users is given
    UB_predicted[i] <- ifelse(is.nan(UB_predicted[i]) == T, mean(sim_to_user$rate), UB_predicted[i])
  }
```


#Matrix Factorization with bias and Regularisation
```{r}
MF_TestPrediction <- function(Movie_rating, test){
  #Movie_rating - the spread data matrix of movie ratings
  #test - vector  of the userIds and Movie Titles set aside to form the test set
  
  
  #H0 and W0 are the bias matrices, that are set to an initial value of 1.
init = list(
  H0 = matrix(1, nrow = 1, ncol = ncol(Movie_rating)),
  W0 = matrix(1, nrow = nrow(Movie_rating), ncol = 1)
)

# matrix factorization with bias included
decomp <- nnmf(A = Movie_rating,
               method = "scd",       #decomposition method is sequential coordinate-wise descent
               k = 3,
               alpha = c(0.001,0,0),  #L2 Regularisation on W 
               beta = c(0.001,0,0),   #L2 Regularisation on H
               init = init, # bias terms
               max.iter = 10000) #Maximum number of iterations

# results
mf_observed <- decomp$W %*% decomp$H  #predicted values of all the movie & user combinations

#This function extracts the predictions of the test set observations.
Prediction <- function(i){ 
  #i is a counter
  user <- as.character(test$userId[i])
  title <- as.character(test$title[i])
  Predicted <- NULL
  
  Predicted[i] <- mf_observed[user, title] #pulls predictions from the mf_observed matrix of the test set
  Predicted[i] <- ifelse(Predicted[i] < 1, 1, Predicted[i]) #if the prediction is less than 1, if should be limited to 1
  Predicted[i] <- ifelse(Predicted[i] > 5 , 5, Predicted[i]) #if the prediction is greater than 5, if should be limited to 5
}


r = nrow(test)
MF_Predicted <- sapply(1:r, Prediction)  #this runs multiple values through the prediction function
 

return(MF_Predicted)
}
```

Fulltest is the function created to run all three prediction methods, combine them to attain an ensembled result, and only output the final RMSE. 

NB: the model predicting the all movie ratings for all users, can be found at the end of this file. 
```{r}
Fulltest <- function(seed, no_of_users, data, no_of_movies){
  #seed - set seed to ensure reproducibility
  #no_of_users - scalar value, the number of users to be sampled at random from the full dataset
  #no_of_movies - scalar value, the number of movies to sample. The movies shall be sampled in descending order to gain as much information as possible
  #data - the dataframe of the movie ratings

  Reduced_Ratings <- Data_Subset(data, no_of_users, no_of_movies, seed)
  
  #Creating the test set
  set.seed(seed) #Using the same seed for all iterations
  testobs <- sample(nrow(Reduced_Ratings),trunc(length(Reduced_Ratings$rating)*0.1)) #sampling 10% of points to form the test set
  
  test <- Reduced_Ratings[testobs,]  #saving the test set and its values
  
  Reduced_Ratings$rating[testobs] <- NA  # setting the test set rating values to NA in the training set for the model to predict
  
  #spreading the ratings into a wide matrix of users and movies
  Movie_rating <- Reduced_Ratings %>% 
    complete(userId, title) %>% 
    select(userId, title, rating) %>% 
    spread(key = title, value = rating)
  
  sorted_users <- as.character(unlist(Movie_rating[,1]))
  Movie_rating <- as.matrix(Movie_rating[,-1])   #removing the first column of userId
  row.names(Movie_rating) <- sorted_users  #labeling the with the userId
  
  user_sim <- cosine_sim(Movie_rating)
  
  
  #User-based filtering method
  predictedA <- NULL

  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])
    title <- as.character(test$title[i])
    sim <- user_sim[user,]
    rate <- Movie_rating[,title]
    
    sim_to_user <- as.data.frame(na.omit(cbind(sim, rate)))
    scaled_sim <- sim_to_user$sim/sum(sim_to_user$sim)
    sim_to_user <- cbind(sim_to_user,scaled_sim)
    predictedA[i] <- crossprod(sim_to_user$rate,scaled_sim)
    predictedA[i] <- ifelse(is.nan(predictedA[i]) == T, mean(sim_to_user$rate), predictedA[i])
  }
  
  
  #Item-based filtering method
  movies_user <- t(Movie_rating)  #transpose the Movie_rating matrix to be used to calculate the similarity between movies
  movie_sim <- cosine_sim(movies_user) #cosine similarity of movies
  
  predictedB <- NULL


  for (i in 1:length(test$userId)){
    user <- as.character(test$userId[i])
    title <- as.character(test$title[i])
    sim <- movie_sim[title,]
    rate <- movies_user[,user]
    
    sim_to_movie <- as.data.frame(na.omit(cbind(sim, rate)))
    scaled_movie_sim <- sim_to_movie$sim/sum(sim_to_movie$sim)
    sim_to_movie <- cbind(sim_to_movie,scaled_movie_sim)
    predictedB[i] <- crossprod(sim_to_movie$rate,scaled_movie_sim)
    predictedB[i] <- ifelse(is.nan(predictedB[i]) == T, mean(sim_to_movie$rate), predictedB[i])
  }
  
  #Matrix Factorization MEthod
  predictedC <- MF_TestPrediction(Movie_rating, test)
  
  #Ensemble Predictions created by averaging the predictions 
  PredictedD <- apply(cbind(predictedA,predictedB, predictedC), 1, mean)
  
  #The RMSE of the final predictions
  RMSE_PredD <- sqrt(sum((PredictedD - test$rating)^2)/length(test$rating))
  return(RMSE_PredD) 
}
```

A simple test of the function
```{r}
tic("test1")
Fulltest(Ratings, no_of_users = 100, no_of_movies = 1000, seed = 100)
toc()
```


```{r}
tic()
#20 seeds to iterate the function through, for 100 users and 1000 movies 
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)

accuracy100users1000movies <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 1000, seed = seed[i]))
accuracy100users1000movies
toc()
```

```{r}
tic()
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)

accuracy500users1000movies <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 1000, seed = seed[i]))
accuracy500users1000movies
toc()
```

```{r}
#run again
tic()
seed <- c(1,5,6,90,101,13,15,17,59,21,123,525,24,29,631,43,35,37,69, 73)

accuracy1000users1000movies <- sapply(1:20,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 1000, seed = seed[i]))
accuracy1000users1000movies
toc()

#tictoc measures how long a task takes to run. 20 iterations of 1000 users took 703 seconds (or approx. 12 mins). For this reason, only 5 ireations were run for subsequent tests.
```

```{r}
tic()
seed <- c(1,101,525,69,73)

accuracy3000users1000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 1000, seed = seed[i]))
accuracy3000users1000movies
toc()
```

```{r}
tic()
seed <- c(1,101,525,69,73)

accuracy5000users1000movies <- sapply(1,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 1000, seed = seed[i]))
accuracy5000users1000movies
toc()
```


```{r}
#combining the summaries of the different iterations 
Range_for_1000movies <- cbind(summary(accuracy100users1000movies),summary(accuracy500users1000movies),summary(accuracy1000users1000movies),summary(accuracy3000users1000movies),summary(accuracy5000users1000movies))
colnames(Range_for_1000movies) <- c("100", "500", "1000", "3000", "5000")

#boxplots of the different user sizes
boxplot(Range_for_1000movies, xlab = "No of Users", ylab = "RMSE", main = "Boxplots of different user counts for 1000 Movies",col = c("blue", "red", "green", "violet" , "yellow" ))
```

```{r}
x_axis = c(100, 500, 1000, 3000, 5000)
plot(x= x_axis, y = Range_for_1000movies[4,], type = "b", pch = 19, ylim = c(0.8, 1.2), lwd = 2, ylab = "RMSE", xlab = "No. of Users", main = "RMSE against the Number of User")
#points(Range_for_1000movies[4,])
lines(x= x_axis, y =Range_for_1000movies[1,], col = "darkgreen", lty = 2)
lines(x= x_axis, y =Range_for_1000movies[5,], col = "firebrick", lty = 2)
axis(1, at = c(1, 2, 3, 4, 5) ,labels=colnames(Range_for_1000movies))
# Add a legend
legend("topright", inset=.02, legend=c("Maximum", "Mean", "Minimum"), box.lty=0,
       col=c("firebrick", "black","darkgreen"), lty= c(2,1,2), lwd= c(1,2,1), cex=0.8, bg='lightblue')
```
It was decided to change the number of movies used. The sizes used were 500, 100 and 2000
```{r}
tic()
seed <- c(1,101,525,69, 73)

accuracy100users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 500, seed = seed[i]))
accuracy500users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 500, seed = seed[i]))
accuracy1000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 500, seed = seed[i]))
accuracy3000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 500, seed = seed[i]))
accuracy5000users500movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 500, seed = seed[i]))
toc()
```

Saving the results recorded so far
```{r}
save(accuracy100users1000movies, accuracy500users1000movies, accuracy1000users1000movies, accuracy3000users1000movies, accuracy5000users1000movies, accuracy100users500movies, accuracy500users500movies, accuracy1000users500movies, accuracy3000users500movies, accuracy5000users500movies, Range_for_1000movies,  file = "data/Results.RData")
load("data/Results.RData")
```

Plotting the results of using 500 movies
```{r}
Range_for_500movies <- cbind(summary(accuracy100users500movies),summary(accuracy500users500movies),summary(accuracy1000users500movies),summary(accuracy3000users500movies),summary(accuracy5000users500movies))
colnames(Range_for_500movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_500movies, xlab = "No of Users", ylab = "RMSE", main = "Boxplots of different user counts for 500 Movies",col = c("blue", "red", "green", "violet" , "yellow" ))
```

```{r}
x_axis = c(100, 500, 1000, 3000, 5000)
plot(x= x_axis, y = Range_for_500movies[4,], type = "b", pch = 19, ylim = c(0.8, 1.1), lwd = 2, ylab = "RMSE", xlab = "No. of Users", main = "RMSE against the Number of User for 500 movies")
lines(x= x_axis, y =Range_for_500movies[1,], col = "blue", lty = 2)
lines(x= x_axis, y =Range_for_500movies[5,], col = "red", lty = 2)
axis(1, at = c(1, 2, 3, 4, 5) ,labels=colnames(Range_for_500movies))
# Add a legend
legend("topright", inset=.02, legend=c("Maximum", "Mean", "Minimum"), box.lty=0,
       col=c("red", "black","blue"), lty= c(2,1,2), lwd= c(1,2,1), cex=0.8, bg='lightblue')
```

Sampling users, with 100 movies
```{r}
tic()
seed <- c(1,101,525,69, 73)

accuracy100users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 100, seed = seed[i]))
accuracy500users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 100, seed = seed[i]))
accuracy1000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 100, seed = seed[i]))
accuracy3000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 100, seed = seed[i]))
accuracy5000users100movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 100, seed = seed[i]))
toc()
```

```{r}
Range_for_100movies <- cbind(summary(accuracy100users100movies),summary(accuracy500users100movies),summary(accuracy1000users100movies),summary(accuracy3000users100movies),summary(accuracy5000users100movies))
colnames(Range_for_100movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_100movies, xlab = "No of Users", col = c("blue", "red", "green", "violet" , "yellow" ))
```

Sampling users, with 2000 movies
```{r}
seed <- c(1,101,525,69, 73)

accuracy100users2000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 100, no_of_movies = 2000, seed = seed[i]))
accuracy500users2000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 500, no_of_movies = 2000, seed = seed[i]))
accuracy1000users2000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 1000, no_of_movies = 2000, seed = seed[i]))
accuracy3000users2000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 3000, no_of_movies = 2000, seed = seed[i]))
accuracy5000users2000movies <- sapply(1:5,function(i) Fulltest(Ratings, no_of_users = 5000, no_of_movies = 2000, seed = seed[i]))
```

```{r}
Range_for_2000movies <- cbind(summary(accuracy100users2000movies),summary(accuracy500users2000movies),summary(accuracy1000users2000movies),summary(accuracy3000users2000movies),summary(accuracy5000users2000movies))
colnames(Range_for_2000movies) <- c("100", "500", "1000", "3000", "5000")
boxplot(Range_for_2000movies, xlab = "No of Users", col = c("blue", "red", "green", "violet" , "yellow" ))
```

```{r}
x_axis = c(100, 500, 1000, 3000, 5000)
plot(x= x_axis, y = Range_for_2000movies[4,], type = "b", pch = 19, ylim = c(0.82, 1.5), lwd = 2, ylab = "RMSE", xlab = "No. of Users", main = "RMSE against the Number of User for 2000 movies")
lines(x= x_axis, y =Range_for_2000movies[1,], col = "blue", lty = 2)
lines(x= x_axis, y =Range_for_2000movies[5,], col = "red", lty = 2)
axis(1, at = c(1, 2, 3, 4, 5) ,labels=colnames(Range_for_2000movies))
# Add a legend
legend("topright", inset=.02, legend=c("Maximum", "Mean", "Minimum"), box.lty=0,
       col=c("red", "black","blue"), lty= c(2,1,2), lwd= c(1,2,1), cex=0.8, bg='lightblue')
```

Checking the progression of the RMSE with respect to the number of movies sampled.The number of movies sampled were 100, 500, 1000 and 2000.
```{r}
RMSE_vs_Movies <- cbind(Range_for_100movies[4,], Range_for_500movies[4,] ,Range_for_1000movies[4,], Range_for_2000movies[4,])

colindex = c("blue", "red", "green", "violet")

#plot of all the different user sizes
plot(x = c(100, 500, 1000, 2000), y = RMSE_vs_Movies[5,], type = "l", ylim = c(0.83,1.5), col = "yellow", main = "RMSE against the Number of Movies", xlab = "Number of Movies", ylab = "RMSE")
for (i in 1:4) {
  lines(x = c(100, 500, 1000, 2000), y = RMSE_vs_Movies[i,], col = colindex[i] )
}

legend("topleft", inset=.02, legend=c("100 users","500 users","1000 users","3000 users","5000 users"), box.lty=1,
       col=c(colindex, "yellow"), lty= 1, cex=0.8)


#plot of all the different user sizes excluding 100 users for a closer look
plot(x = c(100, 500, 1000, 2000), y = RMSE_vs_Movies[5,], type = "l", ylim = c(0.83,0.9), xlim = c(100,2000), col = "yellow", main = "RMSE against the Number of Movies", xlab = "Number of Movies", ylab = "RMSE")
for (i in 2:4) {
  lines(x = c(100, 500, 1000, 2000), y = RMSE_vs_Movies[i,], col = colindex[i] )
}

legend("topleft", inset=.02, legend=c("500 users","1000 users","3000 users","5000 users"), box.lty=1,
       col=c(colindex[2:4], "yellow"), lty= 1, cex=0.8)
```

Full prediction of all movies
```{r}
#Editing the matrix factorization formula to output the full matrix
MF_Prediction <- function(Movie_rating){
  #Movie_rating - the spread data matrix of movie ratings
  
  #H0 and W0 are the bias matrices, that are set to an initial value of 1.
init = list(
  H0 = matrix(1, nrow = 1, ncol = ncol(Movie_rating)),
  W0 = matrix(1, nrow = nrow(Movie_rating), ncol = 1)
)

# matrix factorization with bias included
decomp <- nnmf(A = Movie_rating,
               method = "scd",       #decomposition method is sequential coordinate-wise descent
               k = 3,
               alpha = c(0.001,0,0),  #L2 Regularisation on W 
               beta = c(0.001,0,0),   #L2 Regularisation on H
               init = init, # bias terms
               max.iter = 10000) #Maximum number of iterations

# results
MF_Predicted <- decomp$W %*% decomp$H  #predicted values of all the movie & user combinations
ifelse(MF_Predicted < 1, 1, MF_Predicted)
ifelse(MF_Predicted > 5, 5, MF_Predicted)

return(MF_Predicted)
}

Fullprediction <- function(seed, no_of_users, data, no_of_movies){
  #seed - set seed to ensure reproducibility
  #no_of_users - scalar value, the number of users to be sampled at random from the full dataset
  #no_of_movies - scalar value, the number of movies to sample. The movies shall be sampled in descending order to gain as much information as possible
  #data - the dataframe of the movie ratings

  Reduced_Ratings <- Data_Subset(data, no_of_users, no_of_movies, seed)
  
  #No need for a test set split
  
  #spreading the ratings into a wide matrix of users and movies
  Movie_rating <- Reduced_Ratings %>% 
    complete(userId, title) %>% 
    select(userId, title, rating) %>% 
    spread(key = title, value = rating)
  
  sorted_users <- as.character(unlist(Movie_rating[,1]))
  Movie_rating <- as.matrix(Movie_rating[,-1])   #removing the first column of userId
  row.names(Movie_rating) <- sorted_users  #labeling the with the userId
  
  user_sim <- cosine_sim(Movie_rating)
  
  
  #User-based filtering method
  FullPredictionA <- matrix(0, nrow = nrow(Movie_rating), ncol = ncol(Movie_rating))
  
  for (i in 1:nrow(Movie_rating)){
    for ( j in 1:ncol(Movie_rating)){
  
      sim <- user_sim[i,]
      rate <- Movie_rating[,j]
      
      sim_to_user <- as.data.frame(na.omit(cbind(sim, rate)))
      scaled_sim <- sim_to_user$sim/sum(sim_to_user$sim)
      sim_to_user <- cbind(sim_to_user,scaled_sim)
      FullPredictionA[i,j] <- crossprod(sim_to_user$rate,scaled_sim)
      FullPredictionA[i,j] <- ifelse(is.nan(FullPredictionA[i,j]) == T, mean(sim_to_user$rate), FullPredictionA[i,j])
    }
  }

  #Item-based filtering method
  movies_user <- t(Movie_rating)  #transpose the Movie_rating matrix to be used to calculate the similarity between movies
  movie_sim <- cosine_sim(movies_user) #cosine similarity of movies
  
  FullPredictionB <- matrix(0, nrow = nrow(movies_user), ncol = ncol(movies_user))
  
  for (i in 1:nrow(movies_user)){
    for ( j in 1:ncol(movies_user)){
  
      sim <- movie_sim[i,]
      rate <- movies_user[,j]
      
      sim_to_movie <- as.data.frame(na.omit(cbind(sim, rate)))
      scaled_movie_sim <- sim_to_movie$sim/sum(sim_to_movie$sim)
      sim_to_movie <- cbind(sim_to_movie,scaled_movie_sim)
      FullPredictionB[i,j] <- crossprod(sim_to_movie$rate,scaled_movie_sim)
      FullPredictionB[i,j] <- ifelse(is.nan(FullPredictionB[i,j]) == T, mean(sim_to_movie$rate), FullPredictionB[i,j])
    }
  }
  FullPredictionB <- t(FullPredictionB)
  
  #Matrix Factorization Method
  FullPredictionC <- MF_Prediction(Movie_rating)
  
  #Ensemble Predictions
  FullPredictionD <- (FullPredictionA + FullPredictionBB + FullPredictionC)/3
  
  return(FullPredictionD) 
}
```

An example of how the model would work
```{r}
tic()
Fullprediction(seed = 25, no_of_users = 10, no_of_movies = 10, data = Ratings)
toc()
```

